---
title: "Data Cleaning"
author: "Luke Fields (8385924)"
date: "`r format(Sys.Date(), 'November 28, 2022')`"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

Below are the packages and libraries we are using in this assignment. 
  
```{r setup, message = FALSE}
library(corrplot)
library(klaR) 
library(knitr)
library(MASS)
library(tidyverse)
library(tidymodels)
library(ggplot2)
library("dplyr")
library("yardstick")
library(stringr)
tidymodels_prefer()
student_mh <- read_csv("/Users/lukefields/Desktop/pstat197/vignette-binary-class-bootstrap/data/student_mental_health.csv")
knitr::opts_chunk$set(
	echo = TRUE,
	fig.height = 5,
	fig.width = 7,
	tidy = TRUE,
	tidy.opts = list(width.cutoff = 60)
)
opts_chunk$set(tidy.opts=list(width.cutoff=60),tidy=TRUE)
options(digits = 4)
## indents are for indenting r code as formatted text
## They may need to be adjusted depending on your OS
# if your output looks odd, increase or decrease indent
indent1 = '    '
indent2 = '        '
indent3 = '            '
```

Before we begin working with our model, we will factorize the survived and pclass variables first, making sure that "Yes" is the first level in our data set. 


First, do some string manipulation on year and then turn that column into a factor
```{r}
student_mh <- select(student_mh, -Timestamp)
student_mh$Year <- str_sub(student_mh$Year, -1)
student_mh$Year <- as.numeric(student_mh$Year)
student_mh
```
Also, we do not need timestamp for this assignment

Next, make factors of certain categorical variables
```{r}
student_mh_clean <- student_mh %>%
  mutate(Married = factor(Married, levels = c("Yes", "No")),
         Depression = factor(Depression, levels = c("Yes", "No")),
         Anxiety = factor(Anxiety, levels = c("Yes", "No")),
         Panic_Attack = factor(Panic_Attack, levels = c("Yes", "No")),
         Seek_Help = factor(Seek_Help, levels = c("Yes", "No")),)

write_csv(student_mh_clean, "~/Desktop/pstat197/vignette-binary-class-bootstrap/data/student_mh_clean.csv")
```


```{r}
student_mh_clean %>%
  head()
```


